Visually pleasing knot projections

### 2023-01-31 inst/jma_knot.tex
fixes #93

\begin{figure}[!tbp]
\begin{verbatim}
knotplot2(k7_6,text=TRUE,lwd=1,circ=0,rainbow=TRUE)
\end{verbatim}
 \centering
\includegraphics[scale = 0.9]{knot-004}
\caption{Knot~$7_6$ with strands numbered \label{k76_strands} so that
  the sense of the crossings can be established.  For example, strand
  7 passes over strand 3.  In the package, this fact is specified by
  the {\tt overunder} object, as discussed in the text, having a row
  {\tt 7 3} (and not {\tt 3 7} which would be the crossing having the
  opposite sense).  Crossings become relevant only for the final
  rendering of the knot curve with the gaps included}
\end{figure}

>>>>

\begin{figure}[!tbp]
\begin{verbatim}
knotplot2(k7_6,text=TRUE,lwd=1,circ=0,rainbow=TRUE)
\end{verbatim}
 \centering
\includegraphics[scale = 0.9]{knot-004}
\caption{Knot~$7_6$ with strands numbered \label{k76_strands} so that
  the sense of the crossings can be established.  For example, strand
  7 should pass over strand 3 as per the {\tt overunder}
  specification.  Crossings become relevant only for the final
  rendering of the knot curve with the gaps included}
\end{figure}
